Depression and suicidality as costly signals of need

### 2021-04-20 Paper.rmd
Working on Feedback analysis

Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link, which maps [0, 1] to (-$\infty$, $\infty$). The interaction would also increase the number of parameters to estimate, increasing the risk of overfitting. We therefore did not include it in the GLM models (but we still report OLS models with the interaction term).

@@

```{r feedbackplot, fig.width=9, fig.cap="The distribution of optional feedback provided at the end of the study. None: no feedback provided (includes, e.g., 'none', 'no', 'N/A'). Generic: A few short words, such as 'nice study', or 'thanks'. Attention check: question or comment on the attention checks. Informative: one or two sentences commenting on specific aspects of the survey."}
plot_feedback
```

@@

## Differences between quasibinomial and bootstrapped confidence intervals

>>>>

Although two of our four preregistered OLS regression models included an interaction term, the rationale for it was less convincing for quasibinomial models using a logit link because the expected interaction -- reduced effect of signals in individuals with high baseline belief -- is "built in" to logistic regression (i.e., the effect of a predictor on the outcome necessarily diminishes as the outcome approaches 1). Because our theory does not predict an interaction beyond that already present in a logistic regression model, we did not include an interaction term in the GLM models (but we still report OLS models with the interaction term).

@@

```{r feedbackplot, fig.width=9, fig.cap="The distribution of optional feedback provided at the end of the study. None: no feedback provided (includes, e.g., 'none', 'no', 'N/A'). Generic: A few short words, such as 'nice study', or 'thanks'. Informative: one or two sentences commenting on specific aspects of the survey."}

hagenutils::ggxtabs(xtabs(~Feedback3 + vignette, d), cell_counts = T) + xlab('')
```

```{r informativeplot, fig.width=9, fig.cap="The distribution of informative feedback provided at the end of the study. See Figure \\@ref(fig:feedbackplot) for other types of feedback. See Table \\@ref(tab:informativetab) for all informative statements."}
hagenutils::ggxtabs(xtabs(~Informative + vignette, d), cell_counts = T) + xlab('')
```

```{r informativetab}
d %>% 
  dplyr::select(Informative, vignette, Feedback_original) %>% 
  dplyr::filter(!is.na(Informative)) %>% 
  arrange(Informative, vignette) %>% 
  kable(caption="Informative feedback provided by participants after T3 (the end of the study). Categorization required some judgement calls.") %>% 
  kable_styling()
```

@@

## Comparison of estimates and confidence intervals of GLM, Fractional, and bootstrapped models
